Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-12-21 manuscript/manuscript.tex
Fix unwanted lowercase in density-based fig caption

\begin{figure*}
\centering
\includegraphics[width=\linewidth]
    {figures/density-based-discretization-algorithm.pdf}
\caption{
    Example application of the density-based discretization algorithm to a non-linear
    density function.
    (a) the normalised density function $\rho_n(r')$ (blue), current boundaries of the
    tesseroid (orange dots), and the linear density function $\rho_l(r')$ (orange line).
    The dashed red line represents the maximum density difference $\Delta \rho (r')$ at
    which the tesseroid would be divided (assuming that the
    inequality~\ref{eq:delta-density} is not satisfied).
    (b) second iteration of the algorithm with a new linear density function and maximum
    density difference. The tesseroid would be divided at the depth indicated by the
    dashed red line.
    (c) third iteration of the algorithm.
    (d) final output of the density-based discretization, assuming that all four new
    tesseroids satisfy inequality~\ref{eq:delta-density}.
}
\label{fig:density-discretization-algorithm}
\end{figure*}

>>>>

\begin{figure*}
\centering
\includegraphics[width=\linewidth]
    {figures/density-based-discretization-algorithm.pdf}
\caption{
    Example application of the density-based discretization algorithm to a non-linear
    density function.
    (a) The normalised density function $\rho_n(r')$ (blue), current boundaries of the
    tesseroid (orange dots), and the linear density function $\rho_l(r')$ (orange line).
    The dashed red line represents the maximum density difference $\Delta \rho (r')$ at
    which the tesseroid would be divided (assuming that the
    inequality~\ref{eq:delta-density} is not satisfied).
    (b) Second iteration of the algorithm with a new linear density function and maximum
    density difference. The tesseroid would be divided at the depth indicated by the
    dashed red line.
    (c) Third iteration of the algorithm.
    (d) Final output of the density-based discretization, assuming that all four new
    tesseroids satisfy inequality~\ref{eq:delta-density}.
}
\label{fig:density-discretization-algorithm}
\end{figure*}
